---
title: "Neighborhood Navigation Center"
subtitle: Alameda Park, Santa Barbara
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
runtime: shiny
resource_files:
- .Renviron
---
```{r}
source("nnc_dashboard.R", local = TRUE)
```






Inputs {.sidebar}
======================

This dashboard presents data describing the Neighborhood Navigation Centers in Santa Barbara, California.  It was built in collaboration with [SBACT](https://sbact.org) and the many organizations that make up the Neighborhood Navigation Center.

### 
```{r date_input}
dateRangeInput(inputId = "input_date_range",
               label = "Date range",
               start = min(df_data$survey_date))
```

###
```{r weather_input}
checkboxGroupInput(inputId = "input_weather",
                   label = "Weather",
                   choices = v_weather_levels,
                   selected = v_weather_levels)
```

###
```{r warming_station_input}
checkboxGroupInput(inputId = "input_warming_station",
                   label = "Warming station",
                   choices = v_warming_station_levels,
                   selected = v_warming_station_levels)
```



```{r download_button}
uiOutput("downloadUI")

# Create the actual downloadButton
output$downloadUI <- renderUI( {
  downloadButton("downBtn", "Download data", style = "width:100%; background-color:#63666A; border: none;")
})

# Add download handling
output$downBtn <- downloadHandler(
  filename = function() {
    "nnc.csv"
  },
  content = function(file) {
    write.csv(df_download, file, row.names = FALSE)
  }
)
```

Overview {data-orientation=rows}
======================

Row 
-----------------------------------------------------------------------


### Meals shared
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_meals),
           icon = "fa-fish",
           color = westmont_green)
})
```


### People received a meal
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_people_in_meal_line),
           icon = "fa-user-friends",
           color = westmont_green)
})
```



### People received clothing
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_clothing),
           icon = "fa-tshirt",
           color = westmont_green)
})
```

### Animals received care
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_animals),
           icon = "fa-paw",
           color = westmont_green)
})
```







Row 
-----------------------------------------------------------------------


### Medical encounters
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_med_encounters),
           icon = "fa-user-md",
           color = westmont_green)
})
```

### Showers facilitated
```{r}
renderValueBox({
  valueBox(fn_value_box(df_data, num_showers),
           icon = "fa-shower",
           color = westmont_green)
})
```


### Hygiene kits distributed
```{r, echo = FALSE}
renderValueBox({
  valueBox(fn_value_box(df_data, num_hygiene_kits),
           icon = "fa-signing",
           color = westmont_green)
})
```


### Case management clients served

```{r, echo = FALSE}
renderValueBox({
  valueBox(fn_value_box(df_data, num_case_mgmt_clients),
           icon = "fa-user-plus",
           color = westmont_green)
})
```


### Diversions initiated

```{r, echo = FALSE}
renderValueBox({
  valueBox(fn_value_box(df_data, num_diversions_initiated),
           icon = "fa-rotate-left",
           color = westmont_green)
})
```





Row 
-----------------------------------------------------------------------

### How many volunteers come to the park each week?

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_volunteers)
})
```



### How many organizations come to the park each week?

```{r}
renderPlotly({
  df_data %>%
    fn_filter_weather() %>%
    group_by(survey_date, organization_name) %>%
    summarise() %>%
    group_by(survey_date) %>%
    summarise(my_sum = n()) %>%
    mutate(my_mov_avg = fn_mov_avg(my_sum, 4),
           my_count_tooltip = paste0("Date: ", survey_date,
                                     "<br>Count: ", my_sum),
           my_mov_avg_tooltip = paste0("Date: ", survey_date,
                                     "<br>4wk avg.: ", round(my_mov_avg, digits = 1))
           ) %>%
    fn_filter_dates() %>%
    fn_time_series_subplots(survey_date, my_sum, my_mov_avg, my_count_tooltip, my_mov_avg_tooltip)
  
})
```







Partners {data-orientation=cols}
======================




### Number of volunteer weeks by partner

```{r}
renderPlotly({
  df_data %>%
    fn_filter_weather() %>%
    fn_filter_dates() %>%
    select(survey_date, 
           my_labels = organization_name, 
           my_parents = organization_service) %>%
    
    group_by(my_labels, my_parents) %>%
    summarise(my_values = n()) %>%
    
    bind_rows(
      df_data %>% 
        fn_filter_weather() %>%
        group_by(organization_service, survey_date) %>%
        summarise() %>%
        group_by(my_labels = organization_service) %>%
        summarise(my_values = n(),
                  my_parents = "NUMBER OF<br>SERVICE<br>WEEKS")) %>%
    
    bind_rows(
      df_data %>%
        fn_filter_weather() %>%
        count(survey_date) %>%
        summarise(my_values = n(),
                  my_labels = "NUMBER OF<br>SERVICE<br>WEEKS")) %>%
  
    mutate(my_ids = ifelse(my_parents == "other_service", paste(my_labels, my_parents, sep = " - "), my_labels),
           my_labels = toupper(gsub("_", "<br>", my_labels)),
           my_parents = toupper(gsub("_", "<br>", my_parents)),
           my_ids = toupper(gsub("_", "<br>", my_ids))) %>%
    
    arrange(my_ids) %>%
    plot_ly(
      ids = ~my_ids,
      labels = ~my_labels,
      parents = ~my_parents,
      values = ~my_values,
      type = "sunburst",
      branchvalues = "relative",
      sort = FALSE) %>%
    
    layout(colorway = westmont_colors,
           annotations =
                 list(x = 0.5, 
                      y = 0, 
                      text = "Click a sector to expand",
                      showarrow = FALSE,
                      font=list(size=15))) %>%
    
    plotly::config(displaylogo = FALSE, 
                   modeBarButtons = list(list("toImage")))
    
})
```

### Weekly volunteers by service and partner
```{r}
renderPlotly({
  df_data %>%
    fn_filter_weather() %>%
    fn_filter_dates() %>%
    select(num_volunteers, 
           my_labels = organization_name, 
           my_parents = organization_service) %>%
    
    group_by(my_labels, my_parents) %>%
    summarise(my_values = median(num_volunteers, na.rm = TRUE)) %>%
    
    bind_rows(
      df_data %>% 
        fn_filter_weather() %>%
        group_by(survey_date, organization_service) %>%
        summarise(num_weekly_volunteers = sum(num_volunteers, na.rm = TRUE)) %>%
        filter(num_weekly_volunteers > 0) %>%
        group_by(my_labels = organization_service) %>%
        summarise(my_values = median(num_weekly_volunteers, na.rm = TRUE),
                  my_parents = "MEDIAN<br>WEEKLY<br>VOLUNTEERS")) %>%
    
    bind_rows(
      df_data %>%
        fn_filter_weather() %>%
        group_by(survey_date) %>%
        summarise(num_weekly_volunteers = sum(num_volunteers, na.rm = TRUE)) %>%
        filter(num_weekly_volunteers > 0) %>%
        summarise(my_values = median(num_weekly_volunteers, na.rm = TRUE),
                  my_labels = "MEDIAN<br>WEEKLY<br>VOLUNTEERS")) %>%
  
    mutate(my_ids = ifelse(my_parents == "other_service", paste(my_labels, my_parents, sep = " - "), my_labels),
           my_labels = toupper(gsub("_", "<br>", my_labels)),
           my_parents = toupper(gsub("_", "<br>", my_parents)),
           my_ids = toupper(gsub("_", "<br>", my_ids))) %>%
    
    arrange(my_ids) %>%
    plot_ly(
      ids = ~my_ids,
      labels = ~my_labels,
      parents = ~my_parents,
      values = ~my_values,
      type = "sunburst",
      branchvalues = "relative",
      sort = FALSE) %>%
    
    layout(colorway = westmont_colors,
           annotations =
                 list(x = 0.5, 
                      y = 0, 
                      text = "Click a sector to expand",
                      showarrow = FALSE,
                      font=list(size=15))) %>%
    
    plotly::config(displaylogo = FALSE, 
                   modeBarButtons = list(list("toImage")))
    
})
```




Hospitality {data-orientation=rows}
======================





Row 
-----------------------------------------------------------------------


### Meals shared


```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_meals)
})
```

### Bagged meals shared

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_meal_bags)
})
```

### People served meals

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_people_in_meal_line)
})
```




### Meal share volunteers

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_volunteers, organization_service == "meals")
})
```






Row 
-----------------------------------------------------------------------

### Animals cared for

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_animals)
})
```



### People receiving clothing

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_clothing)
})
```



### Showers facilitated

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_showers)
})
```

### Hygiene kits shared
```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_hygiene_kits)
})
```


Case Management & Compassionate Care {data-orientation=rows}
======================

Row 
-----------------------------------------------------------------------



### Number of case management clients served


```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_case_mgmt_clients)
})
```


### Number of diversions initiated

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_diversions_initiated)
})
```


Row 
-----------------------------------------------------------------------

### Number of indivuals receiving compassionate care

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_ppl_compassionate_care)
})
```



### Number of agency referrals

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_agency_referrals)
})
```






Medical {data-orientation=rows}
======================

Row
-------------------------------------

### Total medical encounters

```{r}
renderPlotly({
  fn_time_series_graph(df_data, num_med_encounters)
})
```

Row
-------------------------------------



### Encounter demographics

```{r}
renderPlotly({
  df_data %>%
  fn_filter_weather() %>%
  fn_filter_dates() %>%
  #filter(organization_service == "healthcare") %>%
  select(num_med_men, num_med_women) %>%
  summarise(female = sum(num_med_women, na.rm = TRUE),
            male = sum(num_med_men, na.rm = TRUE)) %>%
  pivot_longer(cols = c(female, male),
               names_to = "my_labels",
               values_to = "my_values") %>%
  mutate(my_values = 100*my_values / sum(my_values, na.rm = TRUE),
               my_tooltips = paste(round(my_values,1), "%")) -> df_p1
df_data %>%
       fn_filter_weather() %>%
        fn_filter_dates() %>%
        #filter(organization_service == "healthcare") %>%
        select(num_med_caucasian, num_med_black, num_med_hispanic) %>%
        summarise(caucasian = sum(num_med_caucasian, na.rm = TRUE),
                  black = sum(num_med_black, na.rm = TRUE),
                  hispanic = sum(num_med_hispanic, na.rm = TRUE)) %>%
        pivot_longer(cols = c(caucasian, black, hispanic),
                 names_to = "my_labels",
                 values_to = "my_values") %>%
        mutate(my_values = 100*my_values / sum(my_values, na.rm = TRUE),
               my_tooltips = paste(round(my_values,1), "%")) -> df_p2
df_data %>%
        fn_filter_weather() %>%
        fn_filter_dates() %>%
        #filter(organization_service == "healthcare") %>%
        select(num_med_over_65, num_med_under_65) %>%
        summarise(`under 65` = sum(num_med_under_65, na.rm = TRUE),
              `over 65` = sum(num_med_over_65, na.rm = TRUE)) %>%
        pivot_longer(cols = c(`under 65`, `over 65`),
                 names_to = "my_labels",
                 values_to = "my_values") %>%
        mutate(my_values = round(100*my_values / sum(my_values, na.rm = TRUE),1),
               my_tooltips = paste(round(my_values,1), "%")) -> df_p3
  plot_ly() %>%
  add_pie(data = df_p1, labels = ~my_labels, values = ~my_values, name = "gender",
          domain = list(x = c(0, 0.26), y = c(0.1, 1)), 
          textinfo='label+percent', insidetextorientation='radial',
          text = ~my_tooltips, hoverinfo = "text", hole = 0.3) %>%
  add_pie(data = df_p2, labels = ~my_labels, values = ~my_values, name = "race",
          domain = list(x = c(0.36, 0.62), y = c(0.1, 1)), 
          textinfo='label+percent', insidetextorientation='radial',
          text = ~my_tooltips, hoverinfo = "text", hole = 0.3) %>%
  add_pie(data = df_p3, labels = ~my_labels, values = ~my_values, name = "age",
          domain = list(x = c(0.72, 0.98), y = c(0.1, 1)), 
          textinfo='label+percent', insidetextorientation='radial',
          text = ~my_tooltips, hoverinfo = "text", hole = 0.3) %>%
  layout(showlegend = F,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         colorway = westmont_colors,
         annotations = list(
           list(x = 0.13 , y = 0, text = "GENDER", showarrow = F, xref='paper', yref='paper'),
         list(x = 0.5 , y = 0, text = "RACE", showarrow = F, xref='paper', yref='paper'),
         list(x = 0.86 , y = 0, text = "AGE", showarrow = F, xref='paper', yref='paper')
         )) %>%
plotly::config(displaylogo = FALSE,
                   modeBarButtons = list(list("toImage")))
})
            
  
```


```{r, include = FALSE}
renderPlotly({
  df_data %>%
    fn_filter_weather() %>%
    fn_filter_dates() %>%
    #filter(organization_service == "healthcare") %>%
    select(num_med_men, num_med_women) %>%
    summarise(female = sum(num_med_women, na.rm = TRUE),
              male = sum(num_med_men, na.rm = TRUE)) %>%
    pivot_longer(cols = c(female, male),
                 names_to = "my_labels",
                 values_to = "my_values") %>%
    mutate(my_parents = "gender",
           my_values = 100*my_values / sum(my_values, na.rm = TRUE)) %>%
    
    rbind(
      df_data %>%
        fn_filter_weather() %>%
        fn_filter_dates() %>%
        #filter(organization_service == "healthcare") %>%
        select(num_med_caucasian, num_med_black, num_med_hispanic) %>%
        summarise(caucasian = sum(num_med_caucasian, na.rm = TRUE),
                  black = sum(num_med_black, na.rm = TRUE),
                  hispanic = sum(num_med_hispanic, na.rm = TRUE)) %>%
        pivot_longer(cols = c(caucasian, black, hispanic),
                 names_to = "my_labels",
                 values_to = "my_values") %>%
        mutate(my_parents = "race",
               my_values = 100*my_values / sum(my_values, na.rm = TRUE))) %>%
    
    rbind(
      df_data %>%
        fn_filter_weather() %>%
        fn_filter_dates() %>%
        #filter(organization_service == "healthcare") %>%
        select(num_med_over_65, num_med_under_65) %>%
        summarise(`under 65` = sum(num_med_under_65, na.rm = TRUE),
              `over 65` = sum(num_med_over_65, na.rm = TRUE)) %>%
        pivot_longer(cols = c(`under 65`, `over 65`),
                 names_to = "my_labels",
                 values_to = "my_values") %>%
        mutate(my_parents = "age",
               my_values = round(100*my_values / sum(my_values, na.rm = TRUE),1))) %>%
  
    rbind(data.frame(
      my_labels = c("gender", "race", "age"),
      my_parents = c("", "", ""),
      my_values = c(0,0,0))) %>%
    plot_ly(labels = ~my_labels,
            parents = ~my_parents,
            values = ~my_values,
            type = "treemap",
            tiling = list(packing = "dice-slice")) %>%
        layout(colorway = westmont_colors,
               annotations =
                 list(x = 0.5, 
                      y = -0.2, 
                      text = "Click a sector to expand",
                      showarrow = FALSE,
                      font=list(size=15))) %>%
    plotly::config(displaylogo = FALSE,
                   modeBarButtons = list(list("toImage")))
})
```   


### Volunteer role breakdown

```{r}
renderPlotly({
  df_data %>%
    fn_filter_weather() %>%
    fn_filter_dates() %>%
    filter(organization_name == "doctors_without_walls") %>%
    select(Clinicians = num_clinicians, 
           Packs = num_packs, 
           Scribes = num_scribes, 
           CCS = num_ccs, 
           Peacekeepers = num_peacekeepers) %>%
    gather(key = "dww_role", value = "dww_value") %>%
    group_by(dww_role) %>%
    summarise(count = sum(dww_value, na.rm = TRUE)) %>%
    plot_ly(labels = ~dww_role, values = ~count, type = "pie", hole = 0.2,
            textinfo='label+percent',
               insidetextorientation='radial',
            showlegend = FALSE) %>%
    layout(colorway = westmont_colors) %>%
    plotly::config(displaylogo = FALSE,
                   modeBarButtons = list(list("toImage")))
})
```












<style>

.section.sidebar {
background-color: white;
}


.navbar{
background-color: #9D2235;
border-color: #9D2235;
}


.navbar-inverse {
background-color: #9D2235;
border-color: #9D2235;
}

.navbar-inverse .navbar-brand {
color: #ffffff;
}

.navbar-inverse .navbar-brand:hover,
.navbar-inverse .navbar-brand:focus {
color: #ffffff;
background-color: none;
}

.navbar-inverse .navbar-text {

color: #ffffff;

}

.navbar-inverse .navbar-nav > li > a {

color: #ffffff;

}

.navbar-inverse .navbar-nav > li > a:hover,

.navbar-inverse .navbar-nav > li > a:focus {

color: #ffffff;

background-color: #63666A;

}

.navbar-inverse .navbar-nav > .active > a,

.navbar-inverse .navbar-nav > .active > a:hover,

.navbar-inverse .navbar-nav > .active > a:focus {

color: #ffffff;

background-color: #63666A;

}

.navbar-inverse .navbar-nav > .disabled > a,

.navbar-inverse .navbar-nav > .disabled > a:hover,

.navbar-inverse .navbar-nav > .disabled > a:focus {

color: #ffffff;

background-color: transparent;

}

.navbar-inverse .navbar-toggle {

border-color: transparent;

}

.navbar-inverse .navbar-toggle:hover,

.navbar-inverse .navbar-toggle:focus {

background-color: #63666A;

}

.navbar-inverse .navbar-toggle .icon-bar {

background-color: #ffffff;

}

.navbar-inverse .navbar-collapse,

.navbar-inverse .navbar-form {

border-color: #1a6ecc;

}

.navbar-inverse .navbar-nav > .open > a,

.navbar-inverse .navbar-nav > .open > a:hover,

.navbar-inverse .navbar-nav > .open > a:focus {

background-color: #63666A;

color: #ffffff;

}

@media (max-width: 767px) {

.navbar-inverse .navbar-nav .open .dropdown-menu > .dropdown-header {

border-color: #63666A;

}

.navbar-inverse .navbar-nav .open .dropdown-menu .divider {

background-color: #63666A;

}

.navbar-inverse .navbar-nav .open .dropdown-menu > li > a {

color: #ffffff;

}

.navbar-inverse .navbar-nav .open .dropdown-menu > li > a:hover,

.navbar-inverse .navbar-nav .open .dropdown-menu > li > a:focus {

color: #ffffff;

background-color: #63666A;

}

.navbar-inverse .navbar-nav .open .dropdown-menu > .active > a,

.navbar-inverse .navbar-nav .open .dropdown-menu > .active > a:hover,

.navbar-inverse .navbar-nav .open .dropdown-menu > .active > a:focus {

color: #ffffff;

background-color: #63666A;

}

.navbar-inverse .navbar-nav .open .dropdown-menu > .disabled > a,

.navbar-inverse .navbar-nav .open .dropdown-menu > .disabled > a:hover,

.navbar-inverse .navbar-nav .open .dropdown-menu > .disabled > a:focus {

color: #ffffff;

background-color: transparent;

}

}

.navbar-inverse .navbar-link {

color: #ffffff;

}

.navbar-inverse .navbar-link:hover {

color: #ffffff;

}

.navbar-inverse .btn-link {

color: #ffffff;

}

.navbar-inverse .btn-link:hover,

.navbar-inverse .btn-link:focus {

color: #ffffff;-

}

.navbar-inverse .btn-link[disabled]:hover,

fieldset[disabled] .navbar-inverse .btn-link:hover,

.navbar-inverse .btn-link[disabled]:focus,

fieldset[disabled] .navbar-inverse .btn-link:focus {

color: #ffffff;

}


#downBtn {
  width: 100%;
}
</style>